### 2009-08-10 doc/tech_doc/a-rex/arex_tech_doc.tex
Reorganizing doc catalogue and enabling make doc
bring up to date with new features in code

Before giving access to a file already in the cache, the A-REX contacts
the initial file source to check if the user has read permission on
the file. Also file creation or validity times from the original source
are checked to make sure the cached file is fresh enough. If it is
impossible to obtain creation and invalidation times for the file,
it is invalidated 24 hours after download.

@@

\begin{itemize}
\item \textit{control directory} -- In this directory A-REX stores an information
about accepted jobs. It must have full permissions there.\\
A subdirectory called \textit{log} is created there. It is used to
accumulate information about started and finished jobs. This information
is periodically sent to the desired \emph{logger service}(s). For
each job start and stop event, and for each logger service where that
event must be sent, a separate file is written. Once an event is sent,
the corresponding file is deleted.
\end{itemize}

@@

\item \textbf{\textit{maxlod}}\textit{={[}max\_frontend\_jobs {[}emergency\_frontend\_jobs

@@

\begin{itemize}
\item \textbf{\textit{mail}}\textit{=e-mail\_address} -- specifies an email
address \textbf{from} which the notification mails are sent.
\item \textbf{\textit{defaultttl}}\textit{=ttl {[}ttr]} -- specifies the
time in seconds for the SD to be available after job finished (\emph{ttl})
and after job was deleted (\emph{ttr}) due to \emph{ttl}. Defaults
are 7days for \emph{ttl} and 30 days for \emph{ttr}.
\item \textbf{\textit{lrms}}\textit{=default\_lrms\_name default\_queue\_name}
- specifies names for the LRMS and queue. Queue name can also be specified
in the JD (currently it is not allowed to override LRMS by usingon
the JD).
\item \textbf{\textit{session}}\textit{=path} -- specifies path to the directory
in which the SD is created. If the path is {*} the default one is
used -- \textit{\$HOME/.jobs}. In new configuration file this command
is called \textbf{\textit{sessiondir}}.
\item \textbf{\textit{cachedir}}\textit{=path {[}link\_path]} - specifies
a directory to store cached data (see \ref{sec:cache}).\emph{ }Multiple
cache directories may be specified by specifying multiple \emph{cachedir}
commands. Cached data will be distributed evenly over the caches.
Specifying no \emph{cachedir }command or commands with an empty path
disables caching. Optional \textit{link\_path} specifies the path
at which \emph{path} is accessible on computing nodes, if it is different
from the path on the A-REX host. If \textit{link\_path} is set to '.'
files are not soft-linked, nor are per-job links created, but files
are copied to the session directory. In old configuration file this
command is called \textbf{\textit{cache}}.
\item \textbf{\textit{cachesize}}\textit{=high\_mark {[}low\_mark]} - specifies
high and low watermarks for space used by each cache, as a percentage
of the space on the file system on which the cache directory is located.
When the max is exceeded, files will be deleted to bring the used
space down to the min level. It is a good idea to have each cache
on its own separate file system. To turn off this feature, \char`\"{}cachesize\char`\"{}
without parameters can be specified. These cache settings apply to
all caches specified by \emph{cachedir} commands.
\item \textbf{\textit{maxrerun}}\textit{=number} -- specifies maximal number
of times job will be allowed to rerun after it failed at any stage.
Default value is \emph{5}. This only specifies a upper limit. Actual
number is provided in job description and defaults to 0.
\end{itemize}

>>>>

Before giving access to a file already in the cache, the A-REX
contacts the initial file source to check if the user has read
permission on the file. In order to prevent repeated checks on source
files, this authentication information is cached for a limited
time. On passing the check for a cached file, the user's DN is stored
in the \emph{.meta} file, with an expiry time equivalent to the
lifetime remaining for the user's proxy certificate. This means that
the permission check is not performed for this user for this file
until this time is up (usually several hours). File creation and
validity times from the original source are also checked to make sure
the cached file is fresh enough. If the modification time of the
source is later than that of the cached file, the file will be
downloaded again. The file will also be downloaded again if the
modification date of the source is not available, as it is assumed the
cache file is out of date. These checks are not performed if the DN is
cached and is still valid.

@@

\begin{itemize}
\item \textit{control directory} -- In this directory A-REX stores an information
about accepted jobs. It must have full permissions there.\\
A subdirectory called \textit{logs} is created there. It is used to
accumulate information about started and finished jobs. This information
is periodically sent to the desired \emph{logger service}(s). For
each job start and stop event, and for each logger service where that
event must be sent, a separate file is written. Once an event is sent,
the corresponding file is deleted.
\end{itemize}

@@

\item \textbf{\textit{maxload}}\textit{={[}max\_frontend\_jobs {[}emergency\_frontend\_jobs

@@

\begin{itemize}
\item \textbf{\textit{mail}}\textit{=e-mail\_address} -- specifies an email
address \textbf{from} which the notification mails are sent.
\item \textbf{\textit{defaultttl}}\textit{=ttl {[}ttr]} -- specifies the
time in seconds for the SD to be available after job finished (\emph{ttl})
and after job was deleted (\emph{ttr}) due to \emph{ttl}. Defaults
are 7days for \emph{ttl} and 30 days for \emph{ttr}.
\item \textbf{\textit{lrms}}\textit{=default\_lrms\_name default\_queue\_name}
- specifies names for the LRMS and queue. Queue name can also be specified
in the JD (currently it is not allowed to override LRMS by usingon
the JD).
\item \textbf{\textit{sessiondir}}\textit{=path} -- specifies path to the directory
in which the SD is created. If the path is {*} the default one is
used -- \textit{\$HOME/.jobs}.
\item \textbf{\textit{cachedir}}\textit{=path {[}link\_path]} - specifies
a directory to store cached data (see \ref{sec:cache}).\emph{ }Multiple
cache directories may be specified by specifying multiple \emph{cachedir}
commands. Cached data will be distributed evenly over the caches.
Specifying no \emph{cachedir }command or commands with an empty path
disables caching. Optional \textit{link\_path} specifies the path
at which \emph{path} is accessible on computing nodes, if it is different
from the path on the A-REX host. If \textit{link\_path} is set to '.'
files are not soft-linked, nor are per-job links created, but files
are copied to the session directory.
\item \textbf{\textit{cachesize}}\textit{=high\_mark {[}low\_mark]} - specifies
high and low watermarks for space used by each cache, as a percentage
of the space on the file system on which the cache directory is located.
When the max is exceeded, files will be deleted to bring the used
space down to the min level. It is a good idea to have each cache
on its own separate file system. To turn off this feature, \char`\"{}cachesize\char`\"{}
without parameters can be specified. These cache settings apply to
all caches specified by \emph{cachedir} commands.
\item \textbf{\textit{maxrerun}}\textit{=number} -- specifies maximal number
of times job will be allowed to rerun after it failed at any stage.
Default value is \emph{5}. This only specifies a upper limit. Actual
number is provided in job description and defaults to 0.
\end{itemize}
